Application-Level Regression Testing Framework using Jenkins

### 2017-03-07 manuscript/manuscript.tex
Add files via upload
fixed grammar issues

From the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
Had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We are allowing access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting others jobs.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-watchdog-out}
\caption{ IOR watchdog console output }
\label{fig:IOR-watchdog-out}
\end{figure}
For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use plotting feature to produce plots. 
\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={sample YVALUE output file}, label=lst:yvalue]
bwjenkins$ cat myiorREADnumber.dat 
YVALUE=8352.71
\end{lstlisting}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-plot}
\caption{ IOR plot view }
\label{fig:IOR-plot}
\end{figure}
A plot like this helps us with performance baselines and we can quickly react to changes in the software environment or filesystem configuration that adversely impact performance.

@@

An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.  Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and again when back to successful ).
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{mdtest-config-email}
\caption{ mdtest email configuration }
\label{fig:mdtest-config-email}
\end{figure}

>>>>

To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We are allowing access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-watchdog-out}
\caption{ IOR watchdog console output }
\label{fig:IOR-watchdog-out}
\end{figure}
For tests that produce an interesting performance metric like IOR, we save that output to the file format expected by Jenkins and use the plotting feature to produce plots. 
\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={sample YVALUE output file}, label=lst:yvalue]
bwjenkins$ cat myiorREADnumber.dat 
YVALUE=8352.71
\end{lstlisting}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-plot}
\caption{ IOR plot view }
\label{fig:IOR-plot}
\end{figure}
A plot like this helps us with performance baselines and we can quickly react to changes in the software environment or filesystem configuration that adversely impact performance.

@@

An additional best practice is to enable E-mail Notifications to the test author and/or other interested parties.  Setting notifications for unstable builds will trigger an E-mail every time the test state changes (from successful to failing and once again when successful ).
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{mdtest-config-email}
\caption{ mdtest email configuration }
\label{fig:mdtest-config-email}
\end{figure}
